Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-06-12 acknowledgments.tex
added renyue cen changes.

We acknowledge the  many academic institutions that have supported \enzo\
development, including (in alphabetical order)
Columbia University,
Georgia Institute of Technology,
Michigan State University and the MSU Institute for Cyber-Enabled
Research, 
the National Center for Supercomputing Applications, 
the Pennsylvania State University,
 the San Diego Supercomputer Center (through the Strategic Applications
Partner program and the Director’s office),
SLAC National Accelerator Laboratory,
the SLAC/Stanford Kavli Institute for Particle
Astrophysics and Cosmology,  
Southern Methodist University,
Stanford University,
the University of Arizona,
the University of Califoria at San Diego, 
the University of Colorado at Boulder,
the University of Florida,
and the University of Illinois.
We acknowledge support from the Kavli Institute for Theoretical
Physics at Santa Barbara, the Aspen Center for Physics, and the UCLA
Institute for Pure and Applied Mathematics, which have
generously hosted \enzo\ developers through their conference and
workshop programs.

>>>>

We acknowledge the  many academic institutions that have supported \enzo\
development, including (in alphabetical order)
Columbia University,
Georgia Institute of Technology,
Michigan State University and the MSU Institute for Cyber-Enabled
Research, 
the National Center for Supercomputing Applications, 
the Pennsylvania State University,
 the San Diego Supercomputer Center (through the Strategic Applications
Partner program and the Director’s office),
Princeton University,
SLAC National Accelerator Laboratory,
the SLAC/Stanford Kavli Institute for Particle
Astrophysics and Cosmology,  
Southern Methodist University,
Stanford University,
the University of Arizona,
the University of Califoria at San Diego, 
the University of Colorado at Boulder,
the University of Florida,
and the University of Illinois.
We acknowledge support from the Kavli Institute for Theoretical
Physics at Santa Barbara, the Aspen Center for Physics, and the UCLA
Institute for Pure and Applied Mathematics, which have
generously hosted \enzo\ developers through their conference and
workshop programs.

### 2013-06-12 introduction.tex
Adding page break so that all affliations appear.
added renyue cen changes.

Despite this invested expertise, the Eulerian solvers in their
original form have a serious drawback: they do not provide an easy
method of adaptively increasing the spatial and temporal resolution in
small volumes of the simulation. Such flexibility is essential for
following physical processes such as gravitational instability. A
solution to this was first proposed by \citet{Berger89} in the
Computational Fluid Dynamics (CFD) community, and became known as
Structured Adaptive Mesh Refinement (SAMR). The principle is to
adaptively add and modify additional, finer meshes (``grids'') over
regions that require higher resolution. In addition, it is possible to
add other, more advanced physics including -- for the AMR
implementation in the astrophysics code presented in this paper --
comoving coordinates, self-gravity, radiative cooling, chemistry, heat
conduction, collisionless fluids, magnetohydrodynamics, radiation
transport, star formation and a range of other physical effects.

@@

The \enzo\ code has been extensively used over the last two decades in
a wide variety of problems, resulting in the publication of more than
100 peer-reviewed papers based on results obtained with the code. The
variety of astrophysical systems that \enzo\ has been used for include
galaxies \citep{2003ApJ...587...13T, 2012ApJ...749..140H}, galaxy
clusters \citep{Loken02, Xu11, Skillman13}, the interstellar medium
\citep{Slyz05}, the intergalactic medium \citep{Fang01,
2011ApJ...731....6S}, cooling flows \citep{Li12, 2013ApJ...763...38S},
turbulence \citep{Kritsuk04, 2009JPhCS.180a2020K, Collins11}, the
formation of the first stars \citep{ABN02, 2007ApJ...654...66O,
2009Sci...325..601T, Xu08}, and the formation of stars in our own Galaxy
\citep{Collins11, Collins12a}.

>>>>

Despite this invested expertise, the Eulerian solvers in their
original form have a serious drawback: they do not provide an easy
method of adaptively increasing the spatial and temporal resolution in
small volumes of the simulation. Such flexibility is essential for
following physical processes such as gravitational instability. A
solution to this was first proposed by \citet{Berger89} in the
Computational Fluid Dynamics (CFD) community, and became known as
Structured Adaptive Mesh Refinement (SAMR). The principle is to
adaptively add and modify additional, finer meshes (``grids'') over
regions that require higher resolution. In addition, it is possible to
add other, more advanced physics including -- for the AMR
implementation in the astrophysics code presented in this paper --
comoving coordinates, self-gravity, radiative cooling, chemistry, heat
conduction, collisionless fluids, magnetohydrodynamics, radiation
transport, star formation and a range of other physical effects.
\newpage

@@

The \enzo\ code has been extensively used over the last two decades in
a wide variety of problems, resulting in the publication of more than
100 peer-reviewed papers based on results obtained with the code. The
variety of astrophysical systems that \enzo\ has been used for include
galaxies \citep{2003ApJ...587...13T, 2012MNRAS.425..641L, 2012ApJ...749..140H}, galaxy
clusters \citep{Loken02, Xu11, Skillman13}, the interstellar medium
\citep{Slyz05}, the intergalactic medium \citep{Fang01,
2011ApJ...731....6S}, cooling flows \citep{Li12, 2013ApJ...763...38S},
turbulence \citep{Kritsuk04, 2009JPhCS.180a2020K, Collins11}, the
formation of the first stars \citep{ABN02, 2007ApJ...654...66O,
2009Sci...325..601T, Xu08}, and the formation of stars in our own Galaxy
\citep{Collins11, Collins12a}.

### 2013-06-12 ms.tex
Adding Daegene Koh to author list.  He has made a few contributions since Enzo Days 2012.
Use breakurl package to prevent the bitbucket url from overflowing into the margin.
added renyue cen changes.

\usepackage{graphicx, natbib, color, bm}

@@

\begin{abstract}
This paper describes the open-source code \enzo, which uses a
block-structured adaptive mesh refinement to provide high spatial and
temporal resolution for modeling astrophysical fluid flows.  The code
is Cartesian and can be run in 1, 2, and 3 dimensions, and supports a
large variety of physics, including hydrodynamics, ideal and non-ideal
magnetohydrodynamics, N-body dynamics (and, more broadly, self-gravity
of fluids and particles), primordial gas chemistry, optically-thin
radiative cooling of primordial and metal-enriched plasmas, radiation
transport, and cosmological expansion.  In addition to explaining the
algorithms implemented, we present solutions for a wide range of test
problems, demonstrate the code's parallel scaling properties, and
discuss the \enzo\ collaboration's code development methodology.
\end{abstract}

>>>>

\usepackage{graphicx, natbib, color, bm, hyperref, breakurl}

@@

\begin{abstract}
This paper describes the open-source code \enzo, which uses a
block-structured adaptive mesh refinement to provide high spatial and
temporal resolution for modeling astrophysical fluid flows.  The code
is Cartesian and can be run in 1, 2, and 3 dimensions, and supports a
large variety of physics, including hydrodynamics, ideal and non-ideal
magnetohydrodynamics, N-body dynamics (and, more broadly, self-gravity
of fluids and particles), primordial gas chemistry, optically-thin
radiative cooling of primordial and metal-enriched plasmas (as well as
some optically-thick cooling models), radiation
transport, cosmological expansion, and models for star formation and
feedback in a cosmological context.  In addition to explaining the
algorithms implemented, we present solutions for a wide range of test
problems, demonstrate the code's parallel scaling properties, and
discuss the \enzo\ collaboration's code development methodology.
\end{abstract}

### 2013-06-12 numerical-gravity.tex
Minor change to note that PotentialIterations is user-facing and add comment about MaximumParticleRefinementLevel.
added renyue cen changes.

Simply interpolating the potential without feeding it back to higher levels leads to errors in the potential at more refined levels, due to the build-up of errors during the interpolation of coarse boundary values.  In addition, neighboring subgrids are not guaranteed to generate the same potential values because of the lack of a coherent potential solve across the whole hierarchy. In an attempt to partially alleviate this problem, we allow for an iterative procedure across sibling grids, in which the potential values on the boundary of grids can be updated with the potential in `active' regions of neighboring subgrids.  To prevent overshoot, we average the potential on the boundary and allow for (typically) 4 iterations.  This procedure can help in many cases, but does not necessarily produce a coherent solution across all grids and so does not completely solve the problem; we are working on a slower but more accurate method that does a multigrid solve across the whole grid (Reynolds \etal, in preparation).

>>>>

Simply interpolating the potential without feeding it back to higher levels leads to errors in the potential at more refined levels, due to the build-up of errors during the interpolation of coarse boundary values.  In addition, neighboring subgrids are not guaranteed to generate the same potential values because of the lack of a coherent potential solve including the whole grid hierarchy.  In an attempt to partially alleviate this problem, we allow for an iterative procedure across sibling grids, in which the potential values on the boundary of grids can be updated with the potential in `active' regions of neighboring subgrids.  To prevent overshoot, we average the potential on the boundary and allow for (by default) 4 iterations, with the number of iterations determined by a parameter specified at runtime.  This procedure can help in many cases, but does not necessarily produce a coherent solution across all grids and so does not completely solve the problem; we are working on a slower but more accurate method that does a multigrid solve across the whole grid (Reynolds \etal, in preparation).
